\section{Contributions to LAMENT}\label{contributions-to-lament}

\subsection{Preamble}\label{preamble}

Free and open source software development is a collaborative job.
Various people work on the source code, and different people have
different styles of programming. While we value diversity a lot here,
the presence of a unified coding style is essential for everyone to
provide a more comfortable and convenient environment to collaborate.
Therefore, decisions about the style of the code, the way the pull
requests are described, and the way pull requests are merged should be
standardised.

\subsection{General Rules}\label{general-rules}

\begin{itemize}
\tightlist
\item
  Abide by the \href{CODE_OF_CONDUCT.md}{Code of Conduct}. We are very
  strict about this one. We will not tolerate harassment of any
  contributors here.
\end{itemize}

\subsection{Coding style}\label{coding-style}

\begin{itemize}
\tightlist
\item
  We generally follow the
  \href{https://github.com/luarocks/lua-style-guide}{style guidelines of
  LuaRocks}.
\item
  However we have one strict enforcement, use \texttt{local\ function}s
  whenever possible.
\end{itemize}

\subsection{Pull requests}\label{pull-requests}

\begin{itemize}
\tightlist
\item
  Use concise titles for pull requests and describe what it does well.
\item
  (The applicability of this article to forks on external servers not
  guaranteed) GitHub gives us a nice feature called \emph{tags} on pull
  requests. Use the appropriate tags for your pull requests.
\item
  And that's it you will have a large chance for it being merged.
\end{itemize}

\subsection{Commits (for project
administrators)}\label{commits-for-project-administrators}

\begin{itemize}
\tightlist
\item
  \textbf{VERY IMPORTANT:} The only commits on the \texttt{main} branch
  should be created by merges, unless some sort of apocalypse happens.
\item
  \textbf{Always create branches} for your commits and make a
  \textbf{pull request} to the \texttt{main} branch.
\end{itemize}

\subsection{Final notes}\label{final-notes}

\begin{itemize}
\tightlist
\item
  Do not be afraid to ask whenever you need help. We have both
  \href{https://github.com/Sparkles-Laurel/lament/discussions/10}{GitHub
  Discussions} and a
  \href{https://matrix.to/\#/\#lament-contrib:platypus-sandbox.com}{Matrix
  room}
\end{itemize}
